\chapter{Conclusion}
SCU Collab includes the essential features outlined in our requirements and design. It allows Santa Clara students to use their existing Novell accounts to log in and create groups for collaboration. Each group receives their own pages for discussion and events. In the forum, group members can collaborate with one another online at their own convenience. With event listings, they can schedule meeting times to work together in person.

While the core functions outlined in our requirements have been implemented, the system lacks some features that would greatly benefit user experience. For example, providing a method for users to directly communicate with each other or some sort of moderation system to keep users in check (specifically for forum activity). While these extra features may be useful, the current product is  an application that is straightforward and easy to use. 

\section{Future Development}
While we completed the core functionalities of SCU Collab, there are some aspects that we would like to improve, specifically user management. As of now, there is no administrator or moderator role to oversee user activity. This lack of control may lead to unethical usage of the application as previously discussed in the ethical analysis. Other possible changes include improving overall usability based off user feedback as well as enhancing security, since we did not thoroughly test SCU's authentication system. Implementing a complete desktop browser version of our application is another goal we like to implement.